Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-03 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd

Here, we combine tree-ring records covering three droughts (1964-66, 1977, 1999), species functional and hydraulic trait measurments, and forest census data from a 25.6-ha ForestGEO plot in Virginia (USA) to test a series of hypotheses and associated specific predictions (Table 1) designed to yield functional understanding of how tree size, microenrivonment, and species' traits collectively shape drought responses. First, we focus on the role of tree size and its interaction with microenvironement. We confirm that, consistent with most forests globally [@bennett_larger_2015], larger-diameter trees have lower drought resistance in this forest, which is in an ecoregion (Eastern US temperate deciduous) represented by only one study in Bennett et al (2015) (H1.0). We then test hypotheses designed to disentangle the relative importance of tree height (H1.1), crown exposure (H1.2), and root water access, which should be greater for larger trees indry but not perpetually wet microsites (H1.3). Second, we focus on the role of species' functional and hydraulic traits and their interaction with tree height. We hypothesize that drought resistance will follow predicted and observed patterns in relation to wood density, specific leaf area, and ring porosity (P2.1a-c), but that leaf hydraulic traits such as leaf area shrinkage upon dessication and turgor loss point will prove better predictors (P2.1d-e). We then test whether these traits correlate with tree height (P2.2), potentially driving the observed tendency for taller trees to suffer more during drought (P2.3). Finally, we focused on variability among droughts, asking how  community resistance varied across droughts (H3.1) and whether the factors confirming vulnerability or resistance varied across droughts (H3.2).

>>>>

Here, we combine tree-ring records covering three droughts (1964-66, 1977, 1999), species functional and hydraulic trait measurments, and forest census data from a 25.6-ha ForestGEO plot in Virginia (USA) to test a series of hypotheses and associated specific predictions (Table 1) designed to yield functional understanding of how tree size, microenrivonment, and species' traits collectively shape drought responses. First, we focus on the role of tree size and its interaction with microenvironement. We confirm that, consistent with most forests globally [@bennett_larger_2015], larger-diameter trees have lower drought resistance in this forest, which is in an ecoregion represented by only one study in Bennett et al (2015) (H1.0). We then test hypotheses designed to disentangle the relative importance of tree height (H1.1), crown exposure (H1.2), and root water access, which should be greater for larger trees indry but not perpetually wet microsites (H1.3). Second, we focus on the role of species' functional and hydraulic traits and their interaction with tree height. We hypothesize that drought resistance will follow predicted and observed patterns in relation to wood density, specific leaf area, and ring porosity (P2.1a-c), but that leaf hydraulic traits such as leaf area shrinkage upon dehydration and turgor loss point will prove better predictors (P2.1d-e). We then test whether these traits correlate with tree height (P2.2), potentially driving the observed tendency for taller trees to suffer more during drought (P2.3). Finally, we focused on variability among droughts, asking how  community resistance varied across droughts (H3.1) and whether the factors confirming vulnerability or resistance varied across droughts (H3.2).
